### 2021-02-25 architecture.tex
Unify the style of the diagrams

\begin{figure}[h]
\caption{\gls{cnf} graph schema}
\label{fig:CnfSchema}
\centering
\tikzstyle{token} = [rectangle, draw]

@@

\end{tikzpicture}
\end{figure}
\todo{FB: Clean up the diagram.}

>>>>

\begin{figure}[h]
\caption{\gls{cnf} graph schema}
\label{fig:CnfSchema}
\centering

\digraph[scale=0.5]{CnfSchema}{
graph [ranksep=0.3];
node [fontsize=14, shape=box, height=0, width=0];
edge [fontsize=14];

problem;
clause;
%{ rank = same;
predicate;
atom;
equality;
%}
argument;
term;
function;
variable;

problem -> clause [label=< contains >];
clause -> atom:nw [label=< pos >];
clause -> atom:ne [label=< neg >];
clause -> equality:nw [label=< pos >];
clause -> equality:ne [label=< neg >];
clause -> variable [label=< binds >];
atom -> predicate [label=< atom_applies>];
atom -> argument [label=< atom_has >];
equality -> term [label=< equalizes >];
equality -> variable [label=< equalizes >];
argument -> argument [label=< precedes >];
argument -> term [label=< is >];
argument -> variable [label=< is >];
term -> argument [label=< term_has >];
term -> function [label=< term_applies >];
}

\iffalse
\tikzstyle{token} = [rectangle, draw]

@@

\end{tikzpicture}
\fi

\end{figure}
\todo{FB: Clean up the diagram.}
